Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-06-14 index.qmd
add packages

library(flextable)
library(tidyverse)
library(tidyterra)
library(tidymodels)
library(Utilities.Package) 
library(patchwork)
library(sf) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(rnaturalearthhires)
library(ggforce) 
library(patchwork)
library(terra)
library(gt)
library(scales)
library(magick)
library(grid)
library(ggforce)
library(statebins)
library(ggridges)
library(ggspatial)
library(terrainr)
# library(ggpmisc)
library(broom)
library(stars)
library(gmodels)
library(caret)

>>>>

library(flextable)
library(tidyverse)
library(tidyterra)
library(tidymodels)
library(Utilities.Package) 
library(patchwork)
library(sf) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(rnaturalearthhires)
library(ggforce) 
library(patchwork)
library(terra)
library(gt)
library(scales)
library(magick)
library(grid)
library(ggforce)
library(statebins)
library(ggridges)
library(ggspatial)
library(terrainr)
# library(ggpmisc)
library(broom)
library(stars)
library(gmodels)
library(caret)
library(rstudioapi)
